\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-03-01 paper.tex
Update on Overleaf.

>>>>

\uwds distinguishes itself from DyKnow framework ~\cite{de_leng_dyknow:_2016} that have investigated stream reasoning as key a feature for spatial and temporal reasoning because DyKnow aim to address a large variety of data types, which is why auto configurable systems~\cite{leng_towards_2017} based on the semantic are useful where \uwds only distribute one type of geometric(scene tree) and temporal(timeline) models of the environment as explained above.
